Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Clean up text

We use the algorithm \pysr\footnote{\url{https://github.com/MilesCranmer/PySR}} \cite{cranmerPySRFastParallelized2020} for performing symbolic regression.
\pysr is a genetic algorithm-style symbolic regression algorithm
\citep[see][for an early example]{kozaGeneticProgrammingMeans1994}.
Loosely inspired by \textit{eureqa},
\pysr searches the space of trees 
containing a basis set of specified operators, variables, and arbitrary real constants
to find expressions which fit relations in a given dataset.
\pysr uses ``regularized evolution'' for its search strategy 
\cite{realRegularizedEvolutionImage2019,realAutoMLZeroEvolvingMachine2020},
which itself is a variant on classic tournament selection
\cite{brindleGeneticAlgorithmsFunction1980,goldbergComparativeAnalysisSelection1991}.
This algorithm simulates natural selection: each expression is represented by a tree, corresponding to its ``genetic code.''
Expressions are subsampled, and the fittest expression in each group (using a metric which combines accuracy and simplicity) is used to breed new mutated expressions, as well as cross-bred with other top expressions.
\pysr adds several additional techniques onto these classic algorithms, such as explicit constant optimization using the \textit{BFGS} optimization algorithm \cite{fletcherPracticalMethodsOptimization1988}, and an adaptive complexity penalty, while allowing the use of custom operators and losses which is important for this work.

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
        \\
    &\text{for each } c \in \{1, \ldots, 80\},\nonumber\\
    \text{where }\mathcal{L}(s) &= \sum_i \ell(s(\mathbf{x}_i), y_i)
\end{align}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(\mathbf x_i, y_i)\}$ is the dataset
for $\mathbf x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\{1, \ldots, 80\}$.
Complexity is defined here
as a sum of the complexity of each symbol in the expression,
and $\ell(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.
% \todo{What complexities were chosen?}

>>>>

We use the algorithm and software \pysr\footnote{\url{https://github.com/MilesCranmer/PySR}} \cite{cranmerPySRFastParallelized2020} for performing symbolic regression.
\pysr uses a genetic algorithm-style symbolic regression algorithm
\citep[see][for an early example]{kozaGeneticProgrammingMeans1994}.
Loosely inspired by \textit{eureqa},
\pysr searches the space of trees 
containing a basis set of specified operators, variables, and arbitrary real constants
to find expressions which fit relations in a given dataset.
\pysr uses ``regularized evolution'' for its search strategy 
\cite{realRegularizedEvolutionImage2019,realAutoMLZeroEvolvingMachine2020},
which itself is a variant on classic tournament selection
\cite{brindleGeneticAlgorithmsFunction1980,goldbergComparativeAnalysisSelection1991}.
This algorithm simulates natural selection: each expression is represented by a tree, corresponding to its ``genetic code.''
Expressions are subsampled, and the fittest expression in each group (using a metric which combines accuracy and simplicity) is used to breed new mutated expressions, as well as cross-bred with other top expressions.
\pysr adds several additional techniques onto these classic algorithms, such as explicit constant optimization using the \textit{BFGS} optimization algorithm \cite{fletcherPracticalMethodsOptimization1988}, and an adaptive complexity penalty, while allowing the use of custom operators and losses which is important for this work.

Internal to \pysr, a multi-objective optimization problem is solved: the evolution seeks to find expressions which are as accurate as possible, while being as simple as possible.
Formally, for our setting, \pysr solves the following optimization problem:
\begin{align}
    s_c &= 
        \mathop{\arg\min}_{
            \tiny
            \begin{array}{c}s\in\mathcal{S}\\ \abs{s} = c \end{array}
        }
        \mathcal{L}(s),
        \\
    &\text{for each } c \in \{1, \ldots, 80\},\nonumber\\
    \text{where }\mathcal{L}(s) &= \sum_i \ell(s(\mathbf{x}_i), y_i)
\end{align}
where $s$ is an expression, 
$\mathcal{S}$ is a space of possible expressions considered,
$\abs{s}$ is the complexity of an expression $s$,
$\ell$ is the loss function, and $\{(x_i, y_i)\}$ is the dataset
for $x_i$ each input and $y_i$ the label.
The most accurate expression at each $c$, denoted as $s_c$, is computed for a given set range of $c$, which we choose as $c\in\{1, \ldots, 80\}$.
Complexity is defined here
as a sum of the complexity of each symbol in the expression,
and $\ell(\hat{y}_i, y_i) = \qty(\hat{y}_i - y_i)^2$.
% \todo{What complexities were chosen?}
